Effects of Tunable Hydrophobicity on the Collective Hydrodynamics of Janus Particles under Flows

### 2023-03-22 doc/PRF2022/PRF_main.tex
\dot\gamma checks

The sudden jumps in Figures~\ref{fig:s2esummary}(a) and (b) and
commensurate drops in panels (c) and (d) indicate the existence of a
critical shear rate $\gamma_*$. This means that for $\gamma < \gamma_*$,
the JP phase remains intact while for $\gamma > \gamma_*$, the phase
ruptures. For example, the vesicle BL phase has $\gamma_*$ approximately
$0.05$ ns$^{-1}$ under shear flow and TG flow. However, the critical
shear rate is flow-pattern dependent because the striated phase has
$\gamma_* = 0.14$ ns$^{-1}$ under shear flow while $\gamma_* = 0.05$
ns$^{-1}$ under TG flow. Due to variable stress distribution, the
critical shear rate in TG flow likely depends on the cell size parameter
$\lambda$. The disordered bilayer phase does not really possess a
critical shear rate because it already consists of several, disjoint
components. The jump in Figure~\ref{fig:s2esummary}(a) (solid squares)
simply corresponds to disjoint components drifting apart in the shear
flow. The Type II multilamellar phase did not rupture for any of the
shear rates considered.

>>>>

The sudden jumps in Figures~\ref{fig:s2esummary}(a) and (b) and
commensurate drops in panels (c) and (d) indicate the existence of a
critical shear rate $\dot\gamma_*$. This means that for $\dot\gamma < \dot\gamma_*$,
the JP phase remains intact while for $\dot\gamma > \dot\gamma_*$, the phase
ruptures. For example, the vesicle BL phase has $\dot\gamma_*$ approximately
$0.05$ ns$^{-1}$ under shear flow and TG flow. However, the critical
shear rate is flow-pattern dependent because the striated phase has
$\dot\gamma_* = 0.14$ ns$^{-1}$ under shear flow while $\dot\gamma_* = 0.05$
ns$^{-1}$ under TG flow. Due to variable stress distribution, the
critical shear rate in TG flow likely depends on the cell size parameter
$\lambda$. The disordered bilayer phase does not really possess a
critical shear rate because it already consists of several, disjoint
components. The jump in Figure~\ref{fig:s2esummary}(a) (solid squares)
simply corresponds to disjoint components drifting apart in the shear
flow. The Type II multilamellar phase did not rupture for any of the
shear rates considered.
